TGI-spinal-power

### 2022-04-28 analysis/tgispine_lme_power.Rmd
pushing all to git

>>>>

# Running power analysis on simple model
```{r}
# extract fixed effects from the model
tgi_effect <- fixef(model.cold)["manipulationTGI"]
# need to estimate minimum desired effect from the change in slope - considering values can range from 0-100, it might be simpler to think of these effect sizes as a proportion of 100 instead
# tgi_effect = -17.05 would perhaps leave an expected effect size of .17
# change the effect size to effect size of interest
fixef(model.cold)["manipulationTGI"] <- -17

# then run power analysis
powerSim(model.cold)
```
